Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-15 paper.tex
some work on the conclusion

Those time related parameters can not only impact the uncertainty as
physical parameters (for example the cycle lenght impacting the fuel discharge
burnup and composition)

Cycle length impacts the discharge fuel burnup, it also affects
the frequency of the fuel loads, this, as well as the cooling may imply a
uncertainty on the material availability, which could lead to a large
uncertainty.  Those kind of uncertainties will need a special treatment on further
uncertainty analysis.

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition and will to be extended to random
uncertainty.

While the parameters contributing to natural uranium needs and fissile inventory
uncertainties might be obvious, such study allows to estimate each parameters
contribution, it could be less obvious for other parameters, such as
plutonium quality, waste compositions.  Such studies could also provide research
guidance for nuclear archeology works, which aims to precisely estimate past
fissile production by the different nuclear countries.

>>>>

Those time related parameters can not only impact the uncertainty as
physical parameters (for example the cycle length impacting the fuel discharge
burnup and composition)

Cycle length impacts the discharge fuel burnup, it also affects the frequency of
the fuel loads, this, as well as the cooling may imply a uncertainty on the
material availability, which could lead to an artificially large uncertainty.
Those kind of time related uncertainties will require a careful analysis on further
uncertainty analysis, in order to understand and measure accurately their
contributions on uncertainties.

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition. While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and relative
contributions, it has only been applied to systematic uncertainties per
facilities (parameters randomly generated at each new facility deployment).
This kind of study will to be extended to random uncertainty (new parameter
values at each occurrence) and completely systematic uncertainty (shared by all the
facilities of a kind).

While the parameters contributing to natural uranium needs and fissile inventory
uncertainties might be obvious, such study allows to estimate each parameters
contribution, it could be less obvious for other parameters, such as
plutonium quality, waste compositions.  Such studies could also provide research
guidance for nuclear archaeology works, which aims to precisely estimate past
fissile production by the different nuclear countries.
